\documentclass{article}

\bibliographystyle{plainurl}

\usepackage[T1]{fontenc} 
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[ruled,linesnumbered,vlined]{algorithm2e}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{tabu}
\usepackage{todonotes}
\usepackage{tabto}
\usepackage{url}
\usepackage{hyperref}
\usepackage{caption} 
%\usepackage[left=4cm, right=4cm]{geometry}


\title{Call for Verified Proof Checkers}
\author{Please send your proposal to\\[.3em] \mbox{\url{organizers@satcompetition.org}}\\[.3em] by 15th~of~January~2023.}
\date{}

\begin{document}
\maketitle
\thispagestyle{empty}

We are looking for proposals for new proof checkers for the international SAT competitions. 
Your proposal should specify a proof format and include an actual proof checker implementation for that format.
Please provide an empirical evaluation of the performance of your proof checker implementation.
Your proof checker should run in polynomial time in the size of the formula and proof. 
In this regard, your proposal should address the \emph{complexity} of the proposed proof system. 

The proposed checker or checker tool chain must be \emph{formally verified}. 
If you propose a tool chain with preprocessors, it is sufficient to verify only the relevant tools in the chain. 
In your proposal, you should elaborate on the verified properties and the tools or methods used to verify them.
References to previous publications that support your statements are helpful.


%\subsubsection*{Proof-Complexity and Performance}
%\label{sec:perf}
%This includes an brief overview of its relationship to other popular proof systems such as DRAT. %~\cite{Wetzler:2014:DRATtrim}. 
%Clearly specify the benefits and limitations of the proposed proof system in terms of worst-case lower bounds on proof lengths.
%The evaluation should contain a comparison to \texttt{DRAT-trim}~\cite{Wetzler:2014:DRATtrim}~\cite{Tan:2021:CakeLPR}.
%Briefly outline the underlying proof system which is used by the proposed checker. 


%\subsubsection*{Compatibility and Genericity}
%\label{sec:comp}
% and on how well it \emph{integrates} into existing infrastructure and systems.
%The proof format should be easy to adopt by future SAT solvers.
%You should report on how well the proposed checker integrates into the existing pre-dominant infrastructures. 
%A statement on the compatibility of the proposed proof format should encompass if it subsumes DRAT and how much it costs to translate between the two.
%You should also elaborate on the genericity of the proposed proof system, i.e., the extent to which the proposed checker can be used in domains other than SAT. 

%\bibliography{cfvpc}


\end{document}




